Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-05-21 paper.tex
Add Yonglin's new flavor evolution figures, and update captions

\begin{figure}
  \includegraphics[width=\columnwidth]{20171223-potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg-noscat}
  % Plot:   $DIR/RunBA/RunBA-025deg-noscat-production01/potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg.pdf
  % Data:   $DIR/000Mo-025deg-*km/Lev2-e30a200b30-noscat-04
  % Script: $DIR/nu_potentials-production.nb
  % Config: $DIR/RunBA/RunBA-025deg-noscat-production01/nu_potentials-config-production.nb
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/
  \caption{Neutrino oscillation potentials
    along a test trajectory
    originating at the surface of the hypermassive neutron star, and
    proceeding outward along a radial coordinate ray with angle
    $\theta=25^{\circ}$ with respect to the polar axis.
    The trajectory is parameterized by the coordinate length $s$.
    We plot the vacuum potential due to mass-squared differences (gray bands),
    the matter potential $V_e$ due to forward scattering on $e^-$ and $e^+$
    (dark green),
    and the self-interaction potential $V_{\nu\nu,0}$ due to forward
    scattering on ambient neutrinos (light green, solid where positive,
    dashed where negative);
    additionally we plot the $\nu_e$ and $\bar{\nu}_e$ components composing
    the self-interaction potential (light blue and dark blue respectively).
    This calculation was done with scattering turned off.
    The two gray bands at $V\sim10^{-22}$~erg and $V\sim10^{-24}$~erg
    indicating the two vacuum energy scales for 10--30~MeV neutrinos,
    set the positions of possible Mikheyev-Smirnov-Wolfenstein (MSW)
    or nutation resonances \cite{malk2012-mnr_1}.
    Inside the symmetric point at $s\sim100\,{\rm km}$ the total unoscillated
    self-interaction potential $V_{\nu\nu,0}$ is positive,
    i.e.\ $\nu_e$-dominated.
    }
  \label{fig:V_nunu-noscat}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{20171223-potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg-scat}
  % Plot:   $DIR/RunBA/RunBA-025deg-scat-production01/potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg.pdf
  % Data:   $DIR/000Mo-025deg-*km/Lev2-e30a200b30-scat-04
  % Script: $DIR/nu_potentials-production.nb
  % Config: $DIR/RunBA/RunBA-025deg-scat-production01/nu_potentials-config-production.nb
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/
  \caption{Same as Fig.~\ref{fig:V_nunu-noscat},
    but with scattering turned on.
    Unlike the case with scattering turned off,
    here the total unoscillated self-interaction potential $V_{\nu\nu,0}$
    is everywhere negative, i.e.\ $\bar{\nu}_e$-dominated.
    }
  \label{fig:V_nunu-scat}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-survival_prob-scat_nh}
  % Flavor evolution by Yonglin, see emails 11.28.17 and 1.31.18
  % Plot: $DIR/brett4sfnew300-600kmACC12Step2NE30NH012518m12sc.pdf
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/probabilityPotential-production01
  \caption{Neutrino survival probabilities for the \emph{scat} case.
    In the lower panel we reproduce the self-interaction potential $V_{\nu\nu,0}$
    and matter potential $V_e$ from Fig.~\ref{fig:V_nunu-noscat}.
    \footnote{TODO (Yonglin): change colors and symbols to be consistent with
    text and above plots. Of if you can give me the raw data being plotted, I
    can make the plot.}
    In this case the neutrinos undergo a standard MNR transition
    beginning around $r\sim400$~km,
    with the $e$-flavor neutrinos and antineutrinos partially converting to
    $\nu_x$.
  }
  \label{fig:survival-scat}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{20171223-potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg-noscat}
  % Plot:   $DIR/RunBA/RunBA-025deg-noscat-production01/potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg.pdf
  % Data:   $DIR/000Mo-025deg-*km/Lev2-e30a200b30-noscat-04
  % Script: $DIR/nu_potentials-production.nb
  % Config: $DIR/RunBA/RunBA-025deg-noscat-production01/nu_potentials-config-production.nb
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/
  \caption{Neutrino oscillation potentials
    for the \emph{noscat} case
    along a test trajectory
    originating at the surface of the hypermassive neutron star, and
    proceeding outward along a radial coordinate ray with angle
    $\theta=25^{\circ}$ with respect to the polar axis.
    The trajectory is parameterized by the coordinate length $s$.
    We plot the vacuum potential due to mass-squared differences (gray bands),
    the matter potential $V_e$ due to forward scattering on $e^-$ and $e^+$
    (dark green),
    and the self-interaction potential $V_{\nu\nu,0}$ due to forward
    scattering on ambient neutrinos (light green, solid where positive,
    dashed where negative);
    additionally we plot the $\nu_e$ and $\bar{\nu}_e$ components composing
    the self-interaction potential (light blue and dark blue respectively).
    The two gray bands at $V\sim10^{-22}$~erg and $V\sim10^{-24}$~erg
    indicating the two vacuum energy scales for 10--30~MeV neutrinos,
    set the positions of possible Mikheyev-Smirnov-Wolfenstein (MSW)
    or nutation resonances \cite{malk2012-mnr_1}.
    Inside the symmetric point at $s\sim100\,{\rm km}$ the total unoscillated
    self-interaction potential $V_{\nu\nu,0}$ is positive,
    i.e.\ $\nu_e$-dominated.
    }
  \label{fig:V_nunu-noscat}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{20171223-potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg-scat}
  % Plot:   $DIR/RunBA/RunBA-025deg-scat-production01/potentials-Ve_Vnue_Vnua_Vnu-000Mo-025deg.pdf
  % Data:   $DIR/000Mo-025deg-*km/Lev2-e30a200b30-scat-04
  % Script: $DIR/nu_potentials-production.nb
  % Config: $DIR/RunBA/RunBA-025deg-scat-production01/nu_potentials-config-production.nb
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/
  \caption{Same as Fig.~\ref{fig:V_nunu-noscat},
    but for the \emph{scat} case.
    Unlike the case with scattering turned off,
    here the total unoscillated self-interaction potential $V_{\nu\nu,0}$
    is everywhere negative, i.e.\ $\bar{\nu}_e$-dominated.
    }
  \label{fig:V_nunu-scat}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-survival_prob-noscat_ih}
  % Flavor evolution by Yonglin, see emails 5.9.18, 5.16.18
  % Data: $DIR/300-1499kmACC12Step2NE30IH051418m12sc.dat2p
  % Script: $DIR/plot.gp
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/RunBA-025deg-noscat/flavor_evolution
  \caption{Neutrino survival probabilities for the \emph{noscat} case.
    In the lower panel we reproduce the self-interaction potential $V_{\nu\nu,0}$
    and matter potential $V_e$ from Fig.~\ref{fig:V_nunu-noscat}.
    In this case, the neutrinos undergo collective neutrino oscillation
    beginning around $r\sim700$~km,
    with both the electron neutrinos and antineutrinos almost converting to mu
    or tau neutrinos completely.
  }
  \label{fig:survival-noscat}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-survival_prob-scat_ih}
  % Flavor evolution by Yonglin, see emails 5.9.18, 5.16.18
  % Data: $DIR/300-1499kmACC12Step2NE30IH051418m12sc.dat2p
  % Script: $DIR/plot.gp
  % w/ DIR=/Users/mbdeaton/Documents/ResearchGraveyard/NuclearAstrophysics/DataAndVis/20170412-self_interaction_potentials_M12_M12-LS220-M1/Run03/RunBA/RunBA-025deg-scat/flavor_evolution
  \caption{Same as Fig.~\ref{fig:survival-noscat},
    but for the \emph{scat} case.
    In this case the neutrinos undergo a standard MNR transition
    beginning around $r\sim400$~km,
    with the electron neutrinos converting to mu or tau neutrinos almost
    completely,
    and the electron antineutrinos oscillating back to their original flavor
    after partially converting to mu and tau.
  }
  \label{fig:survival-scat}
\end{figure}
